---
author: Lukas Schmoigl
title: Quarto Example
bibliography: bibliography.bib
---


# Example Repo

https://github.com/schmoigl/test-project/

This Quarto file is showcasing what Quarto can do. Everything outside of code chunks is written in **Markdown**, a simple syntax for formatting plain text.

## Links

Write links as `[text](url)`. Options go in curly braces afterwards, e.g. `{target="_blank"}` opens the link in a new tab: [This is a link](https://data-science.wifo.ac.at/lecture-notes/){target="_blank"} to the lecture notes.

Since the output is a web page, you can also write plain HTML: <a href="https://data-science.wifo.ac.at/lecture-notes/">Same link</a>

## Text formatting

One star makes text italic (`*italic*`), two stars make it bold (`**bold**`): *italic text* **bold text**

## Images

Images work like links, but with a `!` in front: `![caption](path)`. Size and alignment are set in curly braces:

![Images](img/wu.svg){width=200 fig-align="left"}

## Divs, classes and IDs

Quarto turns every element into HTML, and you can label elements so that CSS rules (in `style.css`) can target them:

- A **class** (`.name`) can be given to many elements, and every one of them gets the same style.
- An **ID** (`#name`) must be unique on the page and targets exactly one element.
- A **div** (`::: {.name}` … `:::`) is a box that groups several elements, so you can style them together.

Classes and IDs go in curly braces after a link or image. This link has the class `myLink` (green, no underline). Move your mouse over it: the `:hover` rule in `style.css` underlines it and makes it darker:

```markdown
[Link to WIFO](https://www.wifo.ac.at){target="_blank" .myLink}
```

[Link to WIFO](https://www.wifo.ac.at){target="_blank" .myLink}

This link also has the ID `bigLink`, so the `#bigLink` rule makes it bigger as well:

```markdown
[Big link to WIFO](https://www.wifo.ac.at){target="_blank" .myLink #bigLink}
```

[Big link to WIFO](https://www.wifo.ac.at){target="_blank" .myLink #bigLink}

Both logos below have the class `myLogo`, which makes logos 100px wide. The second one sits inside a div with the class `imageContainer`, and the rule `.imageContainer .myLogo` (200px) only applies to logos inside such a div:

```markdown
![Outside the div](img/wu.svg){fig-align="left" .myLogo}

::: {.imageContainer}
![Inside the div](img/wu.svg){fig-align="left" .myLogo}
:::
```

![Outside the div](img/wu.svg){fig-align="left" .myLogo}

::: {.imageContainer}
![Inside the div](img/wu.svg){fig-align="left" .myLogo}
:::

Quarto also comes with built-in classes. For example, `.column-screen-inset` lets content break out of the narrow text column and use (almost) the full screen width. The table in the R section below uses it.

## Formulas

You can write LaTeX (TeX) formulas. Enclose them in `$...$` for a formula within the text, like $x_1 + x_2$, or in `$$...$$` for a centered formula on its own line:

$$ x_1 + x_2 $$

## Citations

References are stored in `bibliography.bib` (linked in the header at the top of this file). Cite them with `@key`, and Quarto adds the reference list at the end of the page automatically: As seen @eppel2024active

## R code

Code chunks start with ```` ```{r} ````. Execution options are set with `#|` at the top of a chunk and control what is run and what is shown:

| Option | What it does |
|---|---|
| `eval: false` | Do not run the code (just show it) |
| `echo: false` | Run the code, but hide it in the output |
| `output: false` | Run the code, but hide all of its results |
| `message: false` | Hide messages (e.g. when loading packages) |
| `warning: false` | Hide warnings |
| `error: true` | Show errors in the output instead of stopping the render |
| `include: false` | Run the code, but hide both code and results |

Options can also be set for the whole document in the header at the top (e.g. `execute: echo: false`). The chunk below shows its code (`echo: true`) but hides the package messages (`message: false`):

```{r}
#| echo: true
#| message: false
library(tidyverse)
library(kableExtra)

data <- read_csv("data/cases.csv")

plot_data <- data %>%
  separate(case_nr, c("court", "case_nr"), ", ") %>%
  group_by(court, month) %>%
  count(name = "cases") %>%
  group_by(court) %>%
  mutate(sum_cases = sum(cases, na.rm = TRUE)) %>%
  filter(sum_cases > 100) %>%
  ungroup()

write_csv(plot_data, "data/plot_data.csv")
```

Without options, both the code and its output (here a table) are shown. The chunk is wrapped in a `::: {.column-screen-inset}` div, so the table uses the full screen width:

::: {.column-screen-inset}

```{r}
plot_data %>%
  filter(row_number() <= 15) %>%
  kable("html")
```

:::

With inline code (`` `{{r}} data$case_nr[1]` ``) results appear directly in the text, so numbers update automatically when the data changes: The first case is the case `{r} data$case_nr[1]`

## Interactive elements (OJS)

OJS chunks (```` ```{ojs} ````) run JavaScript in the reader's browser, so the page stays interactive without a server. Move the slider:

```{ojs}
viewof rating = Inputs.range([1, 10], {value: 5, step: 1, label: "Rating"})
```

I would rate this class `{ojs} rating`

OJS can read the data that the R code saved above:

```{ojs}
raw = FileAttachment("data/plot_data.csv")

plot_data = raw.csv()

plot_data

new Set(plot_data.map(d => d.court))
```

The chart and text below react to the inputs. OJS cells may appear in any order, since they update whenever a value they depend on changes:

```{ojs}
import {vl} from "@vega/vega-lite-api"

vl.markLine()
  .encode(
    vl.x()
      .fieldT("month")
      .axis({ grid: false }),
    vl.y()
      .fieldQ("cases"),
  )
  .data(plot_data.filter(d => d.court == court))
  .width(width - 100)
  .height(300)
//   .config(config)
  .render({ renderer: "svg" })
```

The chart width is set with `.width(width - 100)`. `width` is a built-in OJS value: the width of the page's text column in pixels. It updates whenever the browser window is resized, and everything that uses it (like the chart) is redrawn. We subtract 100 to leave room for the axis labels. Resize your window and watch the number below change:

```{ojs}
width
```

```{ojs}
viewof court = Inputs.select(
  ["BG Favoriten", "BG Fünfhaus"],
  {label: "Select a court: "}
  )

viewof month = Inputs.select(
  ["2008-01-01", "2009-01-01"],
  {label: "Select a year: "}
  )

numberOfCases = plot_data.filter(d => d.court == court && d.month == month).map(d => d.cases)
```

In the `{ojs} court` in the year `{ojs} month` the number of cases was `{ojs} numberOfCases`
