---
author: Lukas Schmoigl
title: Quarto Example
bibliography: bibliography.bib
---


# Example Repo

https://github.com/schmoigl/test-project/

This Quarto file is showcasing what Quarto can do. Everything outside of code chunks is written in **Markdown**, a simple syntax for formatting plain text.

## Links

Write links as `[text](url)`. Options go in curly braces afterwards, e.g. `{target="_blank"}` opens the link in a new tab: [This is a link](https://data-science.wifo.ac.at/lecture-notes/){target="_blank"} to the lecture notes.

Since the output is a web page, you can also write plain HTML: <a href="https://data-science.wifo.ac.at/lecture-notes/">Same link</a>

## Text formatting

One star makes text italic (`*italic*`), two stars make it bold (`**bold**`): *italic text* **bold text**

## Images

Images work like links, but with a `!` in front: `![caption](path)`. Size and alignment are set in curly braces:

![Images](img/wu.svg){width=200 fig-align="left"}

## Formulas

You can write LaTeX (TeX) formulas. Enclose them in `$...$` for a formula within the text, like $x_1 + x_2$, or in `$$...$$` for a centered formula on its own line:

$$ x_1 + x_2 $$

## Citations

References are stored in `bibliography.bib` (linked in the header at the top of this file). Cite them with `@key`, and Quarto adds the reference list at the end of the page automatically: As seen @eppel2024active

## R code

Code chunks start with ```` ```{r} ````. Options are set with `#|` at the top of a chunk, e.g. `#| echo: false` runs the code but hides it in the output:

```{r}
#| eval: true
#| output: true
#| echo: false
library(tidyverse)
library(kableExtra)

data <- read_csv("data/cases.csv")

plot_data <- data %>%
  separate(case_nr, c("court", "case_nr"), ", ") %>%
  group_by(court, month) %>%
  count(name = "cases") %>%
  group_by(court) %>%
  mutate(sum_cases = sum(cases, na.rm = TRUE)) %>%
  filter(sum_cases > 100) %>%
  ungroup()

write_csv(plot_data, "data/plot_data.csv")
```

Without options, both the code and its output (here a table) are shown:

```{r}
plot_data %>%
  filter(row_number() <= 15) %>%
  kable("html")
```

With inline code (`` `{{r}} data$case_nr[1]` ``) results appear directly in the text, so numbers update automatically when the data changes: The first case is the case `{r} data$case_nr[1]`

## Interactive elements (OJS)

OJS chunks (```` ```{ojs} ````) run JavaScript in the reader's browser, so the page stays interactive without a server. Move the slider:

```{ojs}
viewof rating = Inputs.range([1, 10], {value: 5, step: 1, label: "Rating"})
```

I would rate this class `{ojs} rating`

OJS can read the data that the R code saved above:

```{ojs}
raw = FileAttachment("data/plot_data.csv")

plot_data = raw.csv()

plot_data

new Set(plot_data.map(d => d.court))
```

The chart and text below react to the inputs. OJS cells may appear in any order, since they update whenever a value they depend on changes:

```{ojs}
import {vl} from "@vega/vega-lite-api"

vl.markLine()
  .encode(
    vl.x()
      .fieldT("month")
      .axis({ grid: false }),
    vl.y()
      .fieldQ("cases"),
  )
  .data(plot_data.filter(d => d.court == court))
//   .config(config)
  .render({ renderer: "svg" })
```

```{ojs}
viewof court = Inputs.select(
  ["BG Favoriten", "BG Fünfhaus"],
  {label: "Select a court: "}
  )

viewof month = Inputs.select(
  ["2008-01-01", "2009-01-01"],
  {label: "Select a year: "}
  )

numberOfCases = plot_data.filter(d => d.court == court && d.month == month).map(d => d.cases)
```

In the `{ojs} court` in the year `{ojs} month` the number of cases was `{ojs} numberOfCases`
